An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-03-23 reports/manuscript.tex
Update Stuart's affiliation

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} School of Medicine and Health, Sydney University, Sydney, Australia\\\textsuperscript{8} Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} School of Medicine and Health, Sydney University, Sydney, Australia\\\textsuperscript{8} Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland}
